### 2014-02-27 paper/concrete.tex
checkpoint.

Now, we propose the following two-step process to ensure that
TSNI is preserved:
\begin{enumerate}
  \item First, any of the reduction rules of the abstract
  semantics presented in Section~\ref{sec:retrofit} can
  be restricted by adding a predicate $P$ to the premise of
  any rule other than \textsc{I-noStep}.  The predicate $P$
  can depend only on the \textit{erased} configuration
  |erase il ic|, where |il| is the label of the first task
  in the task list.
\end{enumerate}

>>>>

Now, we propose the following two-step process to ensure that
TSNI is preserved:
\Red{We should find a better name for this.}
\begin{definition}[Non-Interference preserving, restricted isomorphism (NPRI)]
  We call an IFC language
  |concreteLang alpha targetLang| (which can be thought of as
  the concrete language) a \textit{non-intereference preserving,
  restricted isomorphism} with regard to the IFC language
  |specLang alpha targetLang|
  (which can be thought of as the abstract language) if the following
  two conditions hold:
  \begin{enumerate}
    \item Any of the reduction rules of the abstract
    semantics |specLang alpha targetLang|
    presented in Section~\ref{sec:retrofit} can
    be restricted by adding a predicate $P$ to the premise of
    any rule other than \textsc{I-noStep}.  The predicate $P$
    can depend only on the \textit{erased} configuration
    |erase il ic|, where |il| is the label of the first task
    in the task list.
    \item The concrete language
    |concreteLang alpha targetLang|
    must be isomorphic to the abstract semantics |specLang alpha targetLang|
    with the additional predicates $P$ on the rules.
  \end{enumerate}
\end{definition}

\begin{theorem}[NPRI implies TSNI]
  If the language |concreteLang alpha targetLang| is a NPRI, then
  |concreteLang alpha targetLang| satisfies TSNI.
\end{theorem}

### 2014-02-27 paper/retrofit.tex
checkpoint.

\caption{Simple ML-like language |targetLang ML|}
\label{fig:ml}
\end{figure}

@@

\begin{definition}[Information-flow control language]
    An information-flow control language L is a tuple |(C, .->,
    erasef l)|, where $c \in |C|$ is the type of machine configurations, |.->| is a
    reduction relation between machine configurations and |erasef l : C .-> tyerase C|
    is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
    configurations |tyerase C|.  For sequential languages, the
    language is augmented with a set of terminal configuration states $V
    \subseteq |C|$ for which there are no possible further transitions.
\end{definition}

\begin{definition}[$l$-equivalence]
    In a language |(C, .->, erasef l)|, two machine configurations
    |memberf (c, c') C| are considered $l$-equivalent (|c ~= c'|)
    if |erase l c = erase l c'|.
\end{definition}

>>>>

\caption{Simple ML-like language |targetLangML|}
\label{fig:ml}
\end{figure}

@@

\begin{definition}[Information-flow control language]
    An information-flow control language |L| is a tuple $(|C|, |C|^*, |.->|,
    |erasef l|)$, where $c \in |C|$ is the type of machine configurations,
    $|C|^*$ is the type of erased machine configurations, |.->| is a
    reduction relation between machine configurations and $|erasef l|$
    is an erasure function from machine configurations to erased machine
    configurations.  For sequential languages, we may also speak of
    values, e.g. a configurations $V \subseteq |C|$ for which there are
    no possible further transitions.
\end{definition}

\begin{definition}[$l$-equivalence]
    Two machine configurations $c$ and $c'$ are considered $l$-equivalent ($c \approx_l c'$)
    if $|erase l c| = |erase l c'|$.
\end{definition}
